UDC 911.3

### 2024-02-13 bel-geo-congress-2024/Conference-paper.Rmd
Proofreading, folder rename

---
title: "UDC 911.3"
subtitle: "Migration of Russian Legal Companies in 2016–23"
author: P. O. Syomin
output: 
  word_document:
    reference_docx: conference-paper-reference.docx
bibliography: refs.bib
csl: "gost-r-7-0-5-2008-numeric-alphabetical-en.csl"
---

@@

The migration of Russian commercial legal companies in 2016–23 is described and analyzed. Distributions by migration count and distance are estimated and visualized, the relationship between company size and migration decision is statistically tested, net migration rates by region are mapped, and top migration paths are listed. It is found that migrations are rare, mostly short-distance (10–50 km). Bigger companies tend to relocate more often. Moscow has probably lost small and inefficient businesses but gained larger and more profitable ones.

@@

***Keywords:*** companies migration, small and medium-sized businesses, legal companies, legal service, service geography, data analysis, open data, Federal Tax Service.

@@

Migration of companies (business relocation) is an important phenomenon of economy and geography. Its first studies date back to the middle of the 20th century, starting from G. McLaughlin and S. Robock's book *Why Industry Moves South* that have described the migration of enterprises from the North of the US and linked it to cheaper labor and smaller activity of labor unions [@McLaughlin1949]. Various aspects of company migration have been studied, including factors (reasons) [@Wu2007], directions (places) [@Rossi2019], and taxation effects [@Kubicova2016].

In Russia, there are few papers about the migration of companies. Existing works focus on relocation as an instrument of tax optimization [@Adigamova2011_en; @Shcherbakova2016_en], skipping the geographical overview and spatial aspects of the phenomenon. So, a spatial analysis of business relocation in Russia is important. This study describes and visualizes the migration of Russian commercial legal companies in 2016–23. The choice of a particular area of economy, that is, legal service, is subjective.

**Data.** A geo-referenced dataset of Russian small and medium-sized businesses (SMBs) with a main activity code equal to 69.10 (activity in the area of law) was generated from the open dumps of SMB registry[^1] with an open source Python CLI application *ru-smb-companies*[^2] developed by the author of this paper. The dataset covers the period from August 2016 to November 2023. According to [@Moiseeva2016_en], by August 2016 in Russia, there were 47000 commercial legal companies, and the dataset contains about `r round(companies_count_08_2016, -3)` companies with the same date. Some legal companies are missing, e. g. large ones that exceed the limit on the revenue or number of employees for SMBs, but 3/4 are present, so the dataset looks reliable and relevant.

@@

**Methods.** Company migration is seen as a change in the address of registration [@Shcherbakova2016_en]. It is narrow and does not account for other ways of relocation (e. g. mergers or reorganization). Also, it is formal, because the change of nominal address does not necessarily reflect the change of actual place of doing business. However, it looks like the best choice for the data available. Descriptive statistics, statistical tests, data visualization, and mapping are used. Technically, the analysis was performed with R programming language (including additional packages). The source code for the analysis is stored in a public repository[^3].

[^3]: https://github.com/PavelSyomin/tax-service-opendata-paper/tree/main/maksakov-readings-conf-2024

@@

A **relationship between the migration decision and the size of the company** is depicted in *Fig. 2*. Migration among small firms is more frequent in comparison to micro-businesses: according to Fisher's exact test, `r ifelse(categories_test$p.value < 0.001, "p < 0.001", paste("p = ", categories_test$p.value))`, and the odds ratio is `r paste0("1 to ", round(1 / categories_test$estimate, 0))`.

@@

A **distribution of migration distance** is shown in *Fig. 3*. The majority of businesses move to small distances (10–50 km), but there is a significant group of long-migrating firms (the distance is about 1000 km).

@@

**The most popular migration paths** (by the count of migrated companies) with summed revenues and employee counts are listed in the **Table**. The first two paths represent the relocation from the two largest cities of Russia to the surrounding regions. The net change in the number of businesses is relatively small. An increase in the number of registered businesses is not necessarily associated with the increase in income or labor force, and vice versa. A positive flow of companies with a negative flow of revenue or labor probably means that arriving businesses are larger and more profitable than those leaving.

@@

**Conclusion.** Migration of legal companies in Russia is a rare phenomenon: only about 2.5% of all businesses in this activity area have changed their nominal location in 2016–23. Small companies, in comparison to micro-businesses, are more likely to relocate: the chances are 4 times higher. Short-distance (10–50 km) migrations are more common than long-distance (~1000 km) ones. Moscow and St. Petersburg regions are at the top by the net migration rate estimated by the count of relocated businesses, while Moscow has lost the highest number of companies. However, it looks like that while losing small and inefficient companies, Moscow attracts more profitable businesses.

>>>>

---
title: "UDC 911.3"
subtitle: "Migration of Russian Legal Companies in 2016–23"
author: P. O. Syomin
output: 
  word_document:
    reference_docx: conference-paper-reference.docx
bibliography: refs.bib
csl: biblio-style.csl
---

@@

The migration of Russian commercial legal companies in 2016–23 is described and analyzed. Distributions by migration count and distance are estimated and visualized, the relationship between company size and migration decision is statistically tested, net migration rate by region is mapped, and top migration paths are listed. It is found that migrations are rare, mostly short-distance (10–50 km). Bigger companies tend to relocate more often. Moscow has probably lost small and inefficient businesses but gained larger and more profitable ones.

@@

***Keywords:*** company migration, small and medium-sized businesses, legal companies, legal service, service geography, data analysis, open data, Federal Tax Service.

@@

Migration of companies (business relocation) is an important phenomenon of economy and geography. Its first studies date back to the middle of the 20th century, starting from G. McLaughlin and S. Robock's book *Why Industry Moves South* that has described the migration of enterprises from the North of the US and linked it to cheaper labor and weaker activity of labor unions [@McLaughlin1949]. Various aspects of company migration have been studied, including factors (reasons) [@Wu2007], directions (places) [@Rossi2019], and taxation effects [@Kubicova2016].

In Russia, there are few papers about the migration of companies. Existing works focus on relocation as an instrument of tax optimization [@Adigamova2011_en; @Shcherbakova2016_en] and do not pay much attention to the geographical overview and spatial aspects of the phenomenon. So, a spatial analysis of business relocation in Russia is needed. This study describes and visualizes the migration of Russian commercial legal companies in 2016–23. The choice of a particular area of economy, that is, legal service, is subjective.

**Data.** A geo-referenced dataset of Russian small and medium-sized businesses (SMBs) with a main activity code equal to 69.10 (activity in the area of law) was generated from the open dumps of SMB registry[^1] with an open source Python CLI application *ru-smb-companies*[^2] developed by the author of this paper. The dataset covers the period from August 2016 to November 2023. According to [@Moiseeva2016_en], by August 2016 in Russia, there were 47000 commercial legal companies, and the dataset contains about `r format(round(companies_count_08_2016, -3), scientific = FALSE)` companies with the same date. Some legal companies are missing, e. g. larger ones that exceed the limit on the revenue or number of employees for SMBs, but 3/4 are present, so the dataset looks reliable and relevant.

@@

**Methods.** Company migration here is seen as a change in the address of registration, like in [@Shcherbakova2016_en]. This definition is narrow and does not account for other ways of relocation (e. g. mergers or reorganization). Also, it is formal, because the change of nominal address does not necessarily reflect the change of actual place of doing business. However, it looks like the best choice for the data available. Descriptive statistics, statistical tests, data visualization, and mapping are used. Technically, the analysis was performed with R programming language (including additional packages). The source code for the analysis is stored in a public repository[^3].

[^3]: https://github.com/PavelSyomin/tax-service-opendata-paper/tree/main/bel-geo-congress-2024

@@

A **relationship between the migration decision and the size of the company** is depicted in *Fig. 2*. Migration among small firms is more frequent in comparison to micro-businesses: according to Fisher's exact test, `r ifelse(categories_test$p.value < 0.001, "*p* < 0.001", paste("*p* = ", categories_test$p.value))`, and the odds ratio is approximately `r paste0("1 to ", round(1 / categories_test$estimate, 0))`.

@@

A **distribution of migration distance** is shown in *Fig. 3*. The majority of businesses move to small distance (10–50 km), but there is a significant group of long-migrating firms (the distance is about 1000 km).

@@

**The most popular migration paths** (by the count of migrated companies) with summed revenue and employee count are listed in the **table**. The first two paths represent the relocation from the two largest cities of Russia to the surrounding regions. The net change in the number of businesses is relatively small. An increase in the number of registered businesses is not necessarily associated with the increase in income or labor force, and vice versa. A positive flow of companies with a negative flow of revenue or labor probably means that arriving businesses are larger and more profitable than those leaving.

@@

**Conclusion.** Migration of legal companies in Russia is a rare phenomenon: only about 2.5% of all businesses in this activity area have changed their nominal location in 2016–23. Small companies, in comparison to micro-businesses, are more likely to relocate: the probability is 4 times higher. Short-distance (10–50 km) migrations are more common than long-distance (~1000 km) ones. Moscow and St. Petersburg regions are at the top by the net migration rate estimated by the count of relocated businesses, while Moscow has lost the highest number of companies. However, it looks like that while losing small and inefficient companies, Moscow attracts more profitable businesses.
